Expectations bias moral evaluations

### 2018-09-04 paper/paper-apa.Rmd
added R version and cites

bibliography      : ["wiw-biblio.bib"]

@@

@@

We analyzed our data by performing Bayesian estimation using the probabilistic programming language Stan [@Carpenter2017]. We tested our preregistered predictions by computing Bayes Factors (i.e. $BF_{01}$) using the hypothesis function in the R package brms. Bayes Factors express the ratio of the probability of data under the null hypothesis to the probability of the data under an alternative hypothesis. Larger Bayes Factors indicate that the data are more likely under the null hypothesis (i.e., that the intercept is not different from zero) than the alternative hypothesis (i.e., that the intercept is different from zero), and vice versa. As Bayes Factors can be influenced by prior choices [@Gelman2017], we performed prior robustness checks to confirm that our conclusions would not depend substantially on the specification of the priors.

>>>>

bibliography      : ["wiw-biblio.bib", "r-references.bib"]

@@

```{r}
my_citations <- cite_r(
  file = "r-references.bib"
  , pkgs = c("tidyverse", "brms", "gridExtra", "papaja")
  , withhold = FALSE
  # , footnote = TRUE
)
```

@@

All analyses were carried out in `r my_citations`. We analyzed our data by performing Bayesian estimation using the probabilistic programming language Stan [@Carpenter2017]. We tested our preregistered predictions by computing Bayes Factors (i.e. $BF_{01}$) using the *hypothesis* function in the R-package *brms* [Version 2.2.0; @R-brms]. Bayes Factors express the ratio of the probability of data under the null hypothesis to the probability of the data under an alternative hypothesis. Larger Bayes Factors indicate that the data are more likely under the null hypothesis (i.e., that the intercept is not different from zero) than the alternative hypothesis (i.e., that the intercept is different from zero), and vice versa. As Bayes Factors can be influenced by prior choices [@Gelman2017], we performed prior robustness checks to confirm that our conclusions would not depend substantially on the specification of the priors.
